*Supplementary Material*

### 2022-02-19 ms/si.Rmd
Output SI2

---
bibliography: 
- `r here::here("ms/si_references.yaml")`
- `r here::here("ms/si_references_other.yaml")`
---

>>>>

---
bibliography: 
- `r here::here("ms/si_references.yaml")`
- `r here::here("ms/si_references_other.yaml")`
- `r here::here("ms/si_references_other.yaml")`
- `r here::here("ms/si_fossils.bib")`
---
